Echoes of Economic Downturn: Investigating the Persistent Impact of the Great Recession on Birth Rates Among Young Americans

### 2024-02-13 outputs/paper/paper.qmd
methodology done

## Methodology
// TODO: Add methodology for cleaning data
The data was processed and cleaned using R[@citeR], a powerful statistical programming language.

>>>>

## Methodology
// TODO: Add methodology for cleaning data

The data was processed and cleaned using R[@citeR], a powerful statistical programming language. Moreover, most of the data in our dataset are previously cleaned in the project we are replicating. Thus, figure 1 directly used data from `outputs/data/fig_1.csv` without any further cleaning necessary as it simply displays the birth rate from 1980 to 2020. Thus, the cleaned data is directly stored to `outputs/data/fig_1.csv` from `inputs/data/fig_1.csv`.

In figure 2, the dataset was imported from `inputs/data/fig_2.csv` and used R[@dpylr] to select the birth rate of the 6 age groups (from 15 to 44). Furthermore, the selected data was renamed using R[@tidyverse] and changed into names that represent the content of the data better. Moreover, these data is then pivoted using R[@tidyverse] in order to be graphed properly using R[@ggplot2].

In figure 3, the first dataset was imported from `inputs/data/fig_3a.csv` and the dataset containing American states information was from R[@mapdata]. The first dataset was first sliced to remove birth rate information regarding the states of Alaska and Hawaii as these two states can't be properly showned in the dataset from R[@mapdata]. Then, a temporary data frame is created with tibble from R[@tidyverse] witht the the abbreviated state names from `inputs/data/fig_3a.csv` and the state full names. Moreover, the abbreviated state name in the first dataset is switched with the state full names using left_join from R[@dpylr], which is then selected and renamed using R[@tidyverse]. After this, the adjusted dataset with the state full names and birth rate is merged with the second dataset that contains the American states information for further graphing.

In all three figures, the library R[@here] were used to ensure file path is accessible in all directories.
